\documentclass[DD.tex]{subfiles}
\begin{document}

\section{Requirements traceability}
Here we map each requirement described in the RASD document with the system components that will provide services to satisfy them.

\begin{itemize}	

	\item {[G1]} Users can be recognised by their credentials.
	\begin{itemize}
		\item {[R1]}, {[R2]} provided by \textit{Login service} interface in \textit{Access manager}.
	\end{itemize} 

	\item {[G2]} Allow users to keep track of their health data.	
	\begin{itemize}
		\item {[R3]}, {[R6]} provided by \textit{Data Handler Service} interface in \textit{Health Sharing Manager}. 
	\end{itemize}
	
	\item {[G3]} Allow users to have access to an overview of their 
	data, including health parameters and performed activities.
	\begin{itemize}
		\item {[R10]} provided by \textit{DBLink Service} interface in \textit{DatabaseLink Manager} module.
	\end{itemize}
	
	\item {[G4]} Allow users to manage their data access policy.
	\begin{itemize}
		\item {[R4]}, {[R5]} provided by \textit{ManageAccess Request Service} interface in \textit{Health Sharing Manager}.
	\end{itemize}
	
	\item {[G5]} Allow users to monitor their performances during 
	workouts.

	
	\item {[G6]} Each time vital signs go below a threshold value, first 
	aid services have to be notified.
	\begin{itemize}
		\item {[R6]} provided by \textit{Data Handler service} interface in \textit{Health Sharing Manager} module.
		\item {[R7]} provided by \textit{SOS service interface} interface in \textit{SOS manager} module. 
	\end{itemize}
		
	\item {[G7]} Allow users to organise running events.
	
	\item {[G8]} Allow third parties to access data.
	\begin{itemize}
		\item {[R8]} The machine has to be able to communicate with 
		third parties. [	TO CLARIFY]
		\item {[R9]} provided by \textit{Anonymous Data Sharing Service} interface in \textit{HealthSharing Manager}.
		\item {[R10]} provided by \textit{DBLink Service} interface in \textit{DatabaseLink Manager} module.
	\end{itemize}
	
\end{itemize}
\newpage

\end{document}